New approaches for boosting to uniformity

### 2014-09-23 assets/paperdraft/parts/metrics.tex
I've added Dto3h metrics result, and merged theil and SDE graphs for my distributions.

\subsection{Advantages and Disadvantages of Different Metrics}
Let us compare two metrics that have proven most appropriate for our problem, SDE and Theil. We have some linearly spaced array of mass of particles
from interval $[0,1]$, some constant $\alpha$ linearly sapced in interval $[.1,1]$. The predictions are correlated with mass via beta distribution.
We have two distributions that are different in a way that they are symmetrical. SDE should show no changes if we flip the distribution, while the Theil should make difference between pit and peak. First distribution with a peak is given by:

@@

\begin{figure}[H]
\centering
	\includegraphics[width=8cm]{graphs/measures1.png}
	\caption{SDE and Theil}
\end{figure}

@@

\begin{figure}[H]
\centering
	\includegraphics[width=8cm]{graphs/measures2.png}
	\caption{SDE and Theil}
\end{figure}

@@

>>>>

\subsection{Advantages and Disadvantages of Different Metrics}
\subsubsection{Theil and SDE}
Let us compare two metrics that have proven most appropriate for our problem, SDE and Theil. We have some linearly spaced array of mass of particles
from interval $[0,1]$, some constant $\alpha$ linearly sapced in interval $[.1,1]$. The predictions are correlated with mass via beta distribution.
We have two distributions that are different in a way that they are symmetrical. SDE should show no changes if we flip the distribution, while the Theil should make difference between pit and peak. First distribution with a peak is given by:

@@

@@

\begin{figure}[H]
\centering
	\includegraphics[width=0.8\textwidth]{graphs/measures_compared.png}
	\caption{SDE and Theil}
\end{figure}

@@

\subsubsection{$D \to hhh$}
When our classifiers where applied to data set $D \to hhh$ we got uniformity measures in a graph below:
\begin{figure}[H]
\centering
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/dto3h_measures_sig.png}
			\caption{Metrics for $D \to hhh$ background}
		\end{subfigure}
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/dto3h_measures.png}
			\caption{Metrics for $D \to hhh$ signal}
		\end{subfigure}
		\caption{Metrics for $D \to hhh$ data set}
\end{figure}

From these graphs we can see the all metrics have shown similar results, and that there is no significant difference on real data sets. SDE and Theil can be used on limit cases to more precisely determine nature of a distribution.
